Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-13 conclusions.tex
Fleshed out future work section a little bit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1068 ccdd05d5-56c1-461a-bf98-85f6876523b4

Although we have demonstrated a feasible method for advance detection we have
not explored the accuracy of sky localization that is possible before merger.
\citet{Fairhurst2009} discusses some of the theoretical prospects for early
sky localization.  Our future work will explore the prospects of early-warning
detection with realistic simulations of binary mergers using the infrastructure
and techniques described here.

@@

%Future work:

%\begin{itemize}
%\item Sub-solar mass search
%\item Hierarchical detection
%\end{itemize}

>>>>

Although we have demonstrated a feasible method for advance detection we have
not yet explored triggering, coincidence, and ranking of gravitational wave
candidates in a framework that supports early \EM\ followup.  If adjacent time slices
have non-negligible cross-correlation with each other, then there may be some
subtleties in the design of these postprocessing stages that we must address in order
to translate the early-warning outputs into candidate events.

Our future work must also address sky localization accuracy prior to merger as well as
observing strategies.  \citep{Fairhurst2009} derives the area of 90\% localization
confidence in terms of timing uncertainties, but it would be advantageous to use
a galaxy catalog to inform the telescope tiling \citep{galaxy-catalog}.  Because
early detection is likely to be especially effective for nearby sources, the galaxy
catalog technique might be an important ingredient in reducing the fraction of
sky that must be imaged.  Extensive injection campaigns and simulations
incorporating realistic binary merger rates will be necessary in order to fully
understand the prospects for early-warning detection, localization, and \EM\ folluwup
using the techniques we have described.

@@
